### 2025-05-06 CO2_response_fitting/Scripts/msuRACiFit_rice_params.Rmd
Update msuRACiFit_rice_params.Rmd

```{r}
#gas_exchange_data <- read_excel("Data/Gas_exchange_measurement_WT_plants.xls")
# ABSOLUTE PATH
gas_exchange_data <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/Gas_exchange_measurement_WT_plants.xls")
```

>>>>

```{r}
#gas_exchange_data <- read_excel("Data/Gas_exchange_measurement_WT_plants.xls")
# ABSOLUTE PATH
gas_exchange_data <- read_excel("C:/Users/xxxx/Data/Gas_exchange_measurement_WT_plants.xls")
```
